### 2024-08-08 NN/plots_preds_latex.tex
commit
zz

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/R2-99.14-Relu2HiddenLayer-HTCflow_rate1-using-conc_nano1-using-Kfluid1-using-heat_flux1-using-X_D1-using-flow_rate2-using-conc_nano2-using-Kfluid2-using-heat_flux2-using-X_D2.png}
    \caption{Prediction of HTC using flow_rate1 conc_nano1 Kfluid1 heat_flux1 X_D1 flow_rate2 conc_nano2 Kfluid2 heat_flux2 X_D2 with Relu2HiddenLayer - R-Squared: 0.94}
\end{figure}

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots_preds/R2-97.09-Tanh1HiddenLayer-Impedance module.png}
    \caption{Prediction of Impedance module with Tanh1HiddenLayer - R-Squared: 0.93}
\end{figure}
